Phenomenological Robotics

### 2011-12-02 draft.tex
Added screwdriver figures to the IKEA scenario.

\documentclass{article}
\usepackage{graphicx}
\usepackage{natbib}

@@

@@

Also, screwdrivers are, supposedly, ``for driving screws''. But what happens
when you a have a flat screwdriver and need to drive a Phillips-head screw? It
is harder to drive it, but have you ever tried driving a flat head screw with a
Phillips screwdriver? It won't work, and you'll start asking yourself what is
wrong, and what you can do to fix it.

You will be having a breakdown, as described by Heidegger, and the screwdriver
will cease to be \emph{ready-to-hand} and become \emph{present-at-hand} until
you can figure out the problem. But how do we equip a robot with the same
capabilities so that it can function in a human world?

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subfig}

@@

% 4. The IKEA scenario.
% (Source: Thesis journal, pages 130 to 139, 17/03/2011)

@@

Also, screwdrivers are, supposedly, ``for driving screws''. But what happens
when you a have a flat screwdriver and need to drive a Phillips-head screw
(Figure~\ref{fig:ikea_flat_phillips})? It is harder to drive it, but have you
ever tried driving a flat head screw with a Phillips screwdriver
(Figure~\ref{fig:ikea_phillips_flat})? It won't work, and you'll start asking
yourself what is wrong, and what you can do to fix it.

\begin{figure}[h]
  \centering
  \subfloat[][Flat screwdriver vs. Phillips-head screw] {
    \includegraphics{figures/ikea_flat_phillips.png}
    \label{fig:ikea_flat_phillips}
  }
  \qquad
  \subfloat[][Phillips screwdriver vs. Flat head screw] {
    \includegraphics{figures/ikea_phillips_flat.png}
    \label{fig:ikea_phillips_flat}
  }
  \caption{The IKEA scenario}
\end{figure}

You will be having a breakdown, as described by Heidegger \cite{dreyfus07}, and
the screwdriver will cease to be \emph{ready-to-hand} and become
\emph{present-at-hand} until you can figure out the problem. But how do we equip
a robot with the same capabilities so that it can function in a human world?
